Mixing time estimation in reversible Markov chains from a single sample path

### 2015-06-01 intro-nips.tex
.

\paragraph{Main results.}
We propose what is apparently the first efficient and fully empirical
estimator of Markov mixing time.
Consider a reversible ergodic Markov chain on $d$ states with spectral
gap $\gap$ (which is well-known to govern mixing time)
and stationary distribution minorized by $\pimin$.
Our main results are summarized as follows.
\begin{enumerate}
  \item
    In \cref{thm:err}, we give an estimator for $\gap$ that
    achieves multiplicative accuracy from \emph{a single sample path}
    of length $\tilde{O}\parens{1/(\pimin\gap^3)}$.\footnote{The
    $\tilde{O}(\cdot)$ notation suppresses logarithmic factors.}
    We also provide an estimator for $\pimin$ that requires a sample
    path of length $\tilde{O}\parens{1/(\pimin\gap)}$.
    However, the valid confidence intervals suggested by
    \cref{thm:err} depend on the unknown quantities $\pimin$ and
    $\gap$.

>>>>

\paragraph{Main results.}
We propose what is apparently the first efficient and fully empirical
estimator of Markov mixing time.
\todod{``apparently'' sounds weak.}
Consider a reversible ergodic Markov chain on $d$ states with spectral
gap $\gap$ (which is well-known to govern mixing time)
and stationary distribution minorized by $\pimin$.
Our main results are summarized as follows.
\begin{enumerate}
  \item
    In \cref{thm:err}, we give an estimator for $\gap$ that
    achieves multiplicative accuracy from \emph{a single sample path}
    of length $\tilde{O}\parens{1/(\pimin\gap^3)}$.\footnote{The
    $\tilde{O}(\cdot)$ notation suppresses logarithmic factors.}
    We also provide an estimator for $\pimin$ that requires a sample
    path of length $\tilde{O}\parens{1/(\pimin\gap)}$.
    However, the valid confidence intervals suggested by
    \cref{thm:err} depend on the unknown quantities $\pimin$ and
    $\gap$.
